### 2025-02-09 data-visualization.qmd
20250208 - marginal density/histogram
20250208 - specify package

```{r}
library("nflplotR")
library("plotly")
library("gghighlight")
library("ggridges")
library("tidyverse")
```

@@

>>>>

```{r}
library("nflplotR")
library("plotly")
library("gghighlight")
library("ggridges")
library("ggExtra")
library("tidyverse")
```

@@

### Marginal Density/Histogram {#sec-scatterplotMarginalDensigram}

```{r}
ggExtra::ggMarginal(
  plot_ypcByPlayerAge,
  type = "densigram")
```
